Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-12 paper/main.tex
Method/Result structure comments

\subsection{Annotation, regressors, contrasts}

\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
``optimal''}

@@

\subsubsection{Annotations \& regressors}

@@

\subsubsection{Contrasts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ingredients" to answer our questions (cf. intro); we have annotations; define
% congruent contrasts based on regressors based on annotations

@@

\section{Results}

>>>>

\subsection{Annotation, regressors, contrasts}
\todo[inline]{why not strip contrasts from this section and call it "Event modeling"?}
\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
``optimal''}

@@

\subsubsection{Annotations \& regressors}
\todo[inline]{maybe call this "annotation" and put 'Audio-description: annotation' and 'movie: annotation' in it together, and have a subsequent section "event models"}

@@

\subsubsection{Contrasts}
\todo[inline]{this should likely move into statistical analysis, and be resolved as an individual section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ingredients" to answer our questions (cf. intro); we have annotations; define
% congruent contrasts based on regressors based on annotations

@@

\section{Results}
\todo[inline]{we have to decide how we want to present this: a) by stimulus or b) by analysis type. With the present abstract I am leaning towards (a), but we should debate that}
